Figures

### 2018-11-05 code/figures.rmd
Changed labels in Figure 3 to lowercase

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
save_plot("../figures/effect-het.png", effect_het,
          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

>>>>

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
effect_het
save_plot("../figures/effect-het.png", effect_het,
          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
